DESIGN OF A TWO-PIECE BRASSIERE CUP TO FIT BREAST DATA POINTS TOWARD ITS AUTOMATION

### 2020-11-23 template/paper/paper_e.tex
Commit1123

%Authors: Please do not make any changes on the commands below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[E]{scitrans}
%\usepackage{graphicx}
\usepackage{math}
\usepackage{bm}
\usepackage[dvipdfmx]{graphicx,xcolor}
\usepackage[dvipdfmx]{epsfig}
%
\appearyear{0000}
\vol{0}
\numberinvol{0}
\setcounter{page}{1}
\setcounter{volumepage}{1}
\Transaction
%%\Shortpaper
\ForSubmission
%Authors: Please do not make any changes on the commands above.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

@@

First, consider the numerical expression of a developable surface constrained by a Gaussian curvature. In general, the normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$ as
\begin{equation}\label{eq:def_kappa_theta}
\kappa_{\theta} = \frac{L \cos^2 \theta + 2M \sin \theta \cos \theta + N \sin^2 \theta}{E \cos^2 \theta + 2F \sin \theta \cos \theta + G \sin^2 \theta}.
\end{equation}
Then the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as

@@

\begin{eqnarray}
\label{eq:GC_expressed_omega}
K &=& -\omega_{\xi} N - \omega_{\zeta}^2, \\
H &=& \disfrac{-\omega_{\xi}+N}{2}.
\end{eqnarray}
A developable surface is defined as a surface with a Gaussian curvature $K = 0$. That is $\kappa_{\min}=0$. TThus, the mean curvature can be calculated as $2H=\kappa_{\max}$. The line direction coinciding with the direction $\mbold{d}_{\min}$ remains straight after a deformation. This straight line is referred to as a generatrix. In this paper, the principal directions are described using the angle $ \alpha $ as 
\begin{eqnarray}\label{eq:d1d2_eq}
\mbold{d}_{\max} &=& \zetavec \cos \alpha + \xivec \sin \alpha, \nonumber \\ 
\mbold{d}_{\min} &=& -\zetavec \sin \alpha + \xivec \cos \alpha.
\end{eqnarray}
The angle $ \alpha $ is referred to as the \textit{rib angle} in this paper.
By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as
\begin{equation}\label{eq:alpha_eq}
\tan \alpha = -\frac{\omega_{\zeta}}{\omega_{\xi}}.
\end{equation}
From \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as 
\begin{equation}\label{eq:kappa1_eq}
\kappa_1 = -\frac{\omega_{\xi}^2 + \omega_{\zeta}^2}{\omega_{\xi}}.
\end{equation}
From above, a developable surface can be determined by $\mbold{\omega}$.
%%%%%%%%%%%%%%ここまで7/21

@@

Let $ \mbold{\psi} = [\omega_{\xi} \;\; \omega_{\eta} \;\; \upsilon] $ be the function vector of a line. Then the vector of the ridge line $ \mbold{\psi}_R $ and the vector of the upper line $ \mbold{\psi}_U $ are represented using Ritz method\cite{c13} as
\begin{equation}\label{eq:R_eq}
\mbold{\psi}_R = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_R}}& \mbold{a}_{\omega_{\eta_R}}& \mbold{a}_{\upsilon_R} \end{array} \right] \cdot \mbold{e}(s_w) = \mbold{a}_R \cdot \mbold{e}(s_w) 
\end{equation}

\begin{equation}\label{eq:U_eq}
\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}}& \mbold{a}_{\omega_{\eta_U}}& \mbold{a}_{\upsilon_U} \end{array} \right] \cdot  \mbold{e}(s_w) = \mbold{a}_U \cdot \mbold{e}(s_w)
\end{equation}
where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods. Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system.

@@

Consequently, this problem can be converted into a nonlinear programming problem, which is solved using the multiplier method and Nelder-Mead method in this study. By solving the nonlinear programming problem, we can design the entire shape of a two-piece brassiere cup.

\section*{SIMULATION AND VERIFICATION}
To demonstrate the utility of our method, we conducted simulations and a verification. For the verification, the infinitesimal rotational ratios vector   of the wire line is given as
\begin{equation}\label{eq:vrf_omgW}
\mbold{\omega}_W = \left[ \begin{array}{ccc}
0 & 2.91 & 0
\end{array}\right]^\mathrm{T}, 
\end{equation}
while the connection point $ \mbold{X}_C $ is given as 
\begin{equation}\label{eq:givenXc}
\mbold{X}_C = \left[ \begin{array}{ccc}
0 & 0.34 & 0.34
\end{array}\right]^\mathrm{T}.
\end{equation}
We prepared two examples of the simulation. Case (1) is a point cloud on a sphere whose radius is set on R by a uniform random number. Case (2) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}. 
The simulations aim to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast” and to confirm that the propose method recreates a given shape. Here, a uniform random number was generated by numpy.random() of Python. \rfig{fig:ObtainedSurfaceNDS}shows the obtained shape and input data for Case (1), where the solid line represents the given wire line. Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.  \rfig{fig:ObtainedSurfaceDS}shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively. Our proposed method produces a cup shape that manifests the function of “fitting to a breast”.

 \rfig{fig:ObtainedSurfaceDS_Pat}. In \rfig{fig:ObtainedSurfaceDS_Pat}, a solid line and a dotted line represent as same as case(1).

\rfig{fig:ObtainedSurfaceNDS_Pat}. In \rfig{fig:ObtainedSurfaceNDS_Pat}, each solid line represents a lower edge and a dotted line represents an upper edge. In this result, we could confirm that the designed cup shape by our proposed method menifests the function:"fitting to a breast".
Next, we show the result in case(2). In
As the calculated shapes approximate the given points, we conclude our proposed method in this paper is useful for efficient design of paper patterns of a two-piece brassiere cup.
\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.eps}
		\label{fig:zx-NDS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.eps}
		\label{fig:zy-NDS}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.eps}
		\label{fig:xy-NDS}
	}
	\caption{Obtained shape and input data points in Case(1)}
	\label{fig:ObtainedSurfaceNDS}
\end{figure}

@@

	\caption{Obtained patterns in Case(2)}
	\label{fig:ObtainedSurfaceDS_Pat}
\end{figure}
\section*{CONCLUSION}
In this paper, we proposed a method to design the cup shape of two-piece brassiere cup and its patterns satisfying the function: "fitting to a breast shape", in case that it is given as a cloud of data points. We claimed the background and problem of design process of a brassiere cup. In design process, as a cup model for check of the shapes of patterns is made of paper, it is assumed that the surface of the model is composed of several developable surfaces. At first, we formulated the cup model based on the differential geometry. And we claimed that a developable surface can be determined by two curves included in it. The design process of a two-piece brassiere cup can be converted to the optimization problem, whose objective function is the error between the cup shape and its data points. In order to calculate the error, we first formulated the error between a point and the surface from geometry condition. Then, we proposed a method to divide a data cloud into two clouds: evaluating the lower cup, or evaluating the upper cup. In order to verification of our proposed method, we prepared two examples of data points: a set of non-developable surface and developable surface. From the result of two examples, we confirmed that our proposed method can design the cup shape which manifests the function. As a result, Our proposed method will be useful for efficient design of a two-piece brassiere cup.

%a this paper, a method to design the cup shape of two-piece brassiere cup and its patterns was proposed when its target shape is given as a cloud of data points. As a cup model for check of the shapes of patterns is made of paper, it is assumed that the surface of the model is composed of several developable surfaces. We claimed that a developable surface can be determined by two curves included in it. The design process of a two-piece brassiere cup can be converted to the optimization problem, whose objective function is the error between the cup shape and its data points. In order to calculate the error, we proposed a method to divide a data cloud into two clouds: evaluated by the lower cup, or evaluated by the upper cup. It was experimentally verified that the cup shape calculated by our proposed method reproduced the given data points well. Our proposed method will be useful for efficient design of not only patterns of a brassiere cup but also plate parts of a structure consisting of developable surfaces.

>>>>

%Authors: Please do not make any changes on the commands below.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[E]{scitrans}
%\usepackage{graphicx}
\usepackage{color}
\usepackage{math}
\usepackage{bm}
%\usepackage[dvipdfmx]{graphicx,xcolor}
\usepackage[dvipdfmx]{epsfig}
%
\appearyear{0000}
\vol{0}
\numberinvol{0}
\setcounter{page}{1}
\setcounter{volumepage}{1}
\Transaction
%%\Shortpaper
\ForSubmission
%Authors: Please do not make any changes on the commands above.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\chcolor{In a study to approximate developable surface, Yang et al. proposed a method to approximate surface with meshes composed of planar quadrilaterals\cite{cX1} and Odeo et al. proposed a method to define the developability of triangle meshes and appoximate them by a set of developable surfaces\cite{cX2}, and Martin et al. proposed a method to reconstruct surfaces by curved forming\cite{cX3}. But all of them only focus on approximating surface by developable surface, which means that they do not refer to the condition of a developable surface itself. When designing a brassiere, it is required to satisfy some conditons of a brassiere cup that designers intend.}

@@

First, consider the numerical expression of a developable surface constrained by a Gaussian curvature. In general, the normal curvature of a direction vector $\mbold{d}_{\theta} = \zetavec \cos \theta + \xivec \sin \theta $ can be described using coefficients of the first and the second fundamental forms $E, F, G, L, M$ and $N$ as
\begin{equation}\label{eq:def_kappa_theta}
\kappa_{\theta} = \frac{L \cos^2 \theta + 2M \sin \theta \cos \theta + N \sin^2 \theta}{E \cos^2 \theta + 2F \sin \theta \cos \theta + G \sin^2 \theta}.
\end{equation}
Then the Gaussian curvature $K$ and the mean curvature $H$, which characterize a surface, can be defined as extreme values of \req{eq:def_kappa_theta}: $ \kappa_{\max} $ and $ \kappa_{\min} $ as follows\cite{cX4}

@@

\begin{eqnarray}
\label{eq:GC_expressed_omega}
K &=& -\omega_{\xi} N - \omega_{\zeta}^2, \\
H &=& \disfrac{-\omega_{\xi}+N}{2}.
\end{eqnarray}
A developable surface is defined as a surface with a Gaussian curvature $K = 0$. That is $\kappa_{\min}=0$. TThus, the mean curvature can be calculated as $2H=\kappa_{\max}$. The line direction coinciding with the direction $\mbold{d}_{\min}$ remains straight after a deformation. This straight line is referred to as a generatrix. In this paper, the principal directions are described using the angle $ \alpha $ as 
\begin{eqnarray}\label{eq:d1d2_eq}
\mbold{d}_{\max} &=& \zetavec \cos \alpha + \xivec \sin \alpha, \nonumber \\ 
\mbold{d}_{\min} &=& -\zetavec \sin \alpha + \xivec \cos \alpha.
\end{eqnarray}
The angle $ \alpha $ is referred to as the \textit{rib angle} in this paper.
By solving $ \kappa_{\theta} = 0 $,　the rib angle $ \alpha $ can be calculated as
\begin{equation}\label{eq:alpha_eq}
\tan \alpha = -\frac{\omega_{\zeta}}{\omega_{\xi}}.
\end{equation}
From \req{eq:GC_expressed_omega}, $\kappa_1$ is calculated as 
\begin{equation}\label{eq:kappa1_eq}
\kappa_1 = -\frac{\omega_{\xi}^2 + \omega_{\zeta}^2}{\omega_{\xi}}.
\end{equation}
From above, a developable surface can be determined by $\mbold{\omega}$.

@@

\chcolor{From above, a curve can be determined by $ \omega_{\xi} ,\omega_{\eta}$ and $\upsilon$.} Let $ \mbold{\psi}$ be a set of functions of $[\omega_{\xi} \;\; \omega_{\eta} \;\; \upsilon] $. \chcolor{Then a set of functions of the ridge line $ \mbold{\psi}_R $ and a set of functions of the upper line $ \mbold{\psi}_U $ are parameterized by using Ritz method\cite{c13} as}
\begin{equation}\label{eq:R_eq}
\mbold{\psi}_R = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_R}} \cdot \mbold{e}(s_w) & \mbold{a}_{\omega_{\eta_R}} \cdot \mbold{e}(s_w)& \mbold{a}_{\upsilon_R} \cdot \mbold{e}(s_w) \end{array} \right]
\end{equation}

\begin{equation}\label{eq:U_eq}
\mbold{\psi}_U = \left[ \begin{array}{ccc} \mbold{a}_{\omega_{\xi_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\omega_{\eta_U}} \cdot  \mbold{e}(s_w) & \mbold{a}_{\upsilon_U} \cdot  \mbold{e}(s_w)  \end{array} \right]
\end{equation}
where $ \mbold{e}_i(s) $ is composed of trigonometric functions with different periods. Let $ \mbold{\Phi}_0 = [\xivec_0^\mathrm{T} \;\; \etavec_0^\mathrm{T} \;\; \zetavec_0^\mathrm{T}] $ be the initial basis of the objective coordinate system.

@@

Consequently, this problem can be converted into a nonlinear programming problem of $ \mbold{a} $, which is solved using the multiplier method and Nelder-Mead method in this study. By solving the nonlinear programming problem, we can design the entire shape of a two-piece brassiere cup.

\section*{SIMULATION AND VERIFICATION}
To demonstrate the utility of our method, we conducted simulations and a verification. For the verification, the infinitesimal rotational ratios vector   of the wire line is given as
\begin{equation}\label{eq:vrf_omgW}
\mbold{\omega}_W = \left[ \begin{array}{ccc}
0 & 2.91 & 0
\end{array}\right]^\mathrm{T}, 
\end{equation}
while the connection point $ \mbold{X}_C $ is given as 
\begin{equation}\label{eq:givenXc}
\mbold{X}_C = \left[ \begin{array}{ccc}
0 & 0.34 & 0.34
\end{array}\right]^\mathrm{T}.
\end{equation}
We prepared three examples of the simulation. Case (1) is a point cloud on a set of a developable surface by a uniform random number using \req{eq:Sur_eq}. Case (2) is a point cloud on a sphere whose radius is set on R by a uniform random number. \chcolor{Case (3) is a point cloud on a measured shape of a torso, which is a representative breast shape.}
The simulations aim to confirm that the propose method recreates a given shape and to verify whether a two-piece brassiere cup can be designed to approximate an undevelopable surface that manifests the function of “fitting to a breast”.

\rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (1), where the solid line represents the given wire line. Each dotted line denotes the calculated generatrices of the cup shape, and each dot represents a data point.  \rfig{fig:ObtainedSurfaceNDS_Pat} shows the obtained pattern where the solid and dotted lines denote the lower and upper edges, respectively. 
Next, a uniform random number was generated by numpy.random() of Python. \rfig{fig:ObtainedSurfaceNDS} shows the obtained shape and input data for Case (2), \chcolor{and \rfig{fig:ObtainedSurfaceNDS2} shows the obtained shape and input data for Case (3) Table \ref{tbl:error and calc} shows the error and calculation time of each case. }

\chcolor{From the result of case(1), we confirm that our proposed method can recreate a given shape as a two-piece brassire cup. And From the result of case(2) and (3), we confirm that our proposed method also can design a two-piece brassiere cup to approximate data points under the conditions.}

Hence, we conclude our proposed method in this paper is useful for the efficient design of paper patterns of a two-piece brassiere cup.
\begin{table}[!h]
	\centering
	\begin{tabular}{|c|c|c|c|} \hline
		& Error & Time[sec] \\ \hline
		case(1) & 0.10 & 1802 \\ \hline
		case(2) & 0.12 & 740 \\ \hline
		case(3) & 1.04& 1682 \\ \hline
	\end{tabular}
	\caption{The error and calculation time of our proposed method in each case.}
	\label{tbl:error and calc}
\end{table}

\begin{figure}[h]
	\centering
	\subfigure[zx-view]{
		\includegraphics[width=0.6\columnwidth,clip]{./figure/NDS/ObtainedRidgeLinefromz-x.eps}
		\label{fig:zx-NDS}
	}
	\hfil
	\subfigure[zy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromz-y.eps}
		\label{fig:zy-NDS}
	}
	\hfil
	\subfigure[xy-view]{
		\includegraphics[width=0.6\columnwidth]{./figure/NDS/ObtainedRidgeLinefromx-y.eps}
		\label{fig:xy-NDS}
	}
	\caption{Obtained shape and input data points in Case(1)}
	\label{fig:ObtainedSurfaceNDS}
\end{figure}

@@

	\caption{Obtained patterns in Case(2)}
	\label{fig:ObtainedSurfaceDS_Pat}
\end{figure}
\section*{CONCLUSION}
\subsection*{Summary}
Herein we propose a method to design the shape of a two-piece brassiere cup and its patterns to satisfy the function of "fitting to a breast shape" when the shape is given as a cloud of data points. In the typical design process, a cup model is made of paper to verify the pattern shape. Our model assumes that the model surface is comprised of several developable surfaces. First, we formulate the cup model based on differential geometry and hypothesize that a developable surface can be determined by two curves included in it. Hence, the design process of a two-piece brassiere cup can be converted into an optimization problem, whose objective function is the error between the cup shape and its data points. To calculate the error, first the error between a point and the surface from the geometry condition is formulated. Second, our proposed method divides the data cloud into two: the lower and upper cups. Then the cups are evaluated. To verify our proposed method, we assessed two cases. One is a non-developable surface, and the other is a developable surface. The results confirm that the proposed method can design a cup shape, which manifests the intended function. Consequently, our proposed method should be useful to efficiently design a two-piece brassiere cup. 
\subsection*{Limitation and Future Work}
\chcolor{Though we proposed a method to design the shape of a two-piece brassiere cup and its patterns to satisfy the function of "fitting to a breast shape" when the shape is given as a cloud of data points, there is still two questions from the point of view of real-world applications. One is whether the brassire cup should cover the breast shape. A brassire cup has several demands, which include the function to form the ideal breast shape. So the function of "fitting to a breast shape" does not only mean fitting to a breast shape itself, but also fitting to an ideal breast shape one wants. For future work, it is required to quantify how much fitting to a breast shape and design the brassire cup shape satisfying it.}
%a this paper, a method to design the cup shape of two-piece brassiere cup and its patterns was proposed when its target shape is given as a cloud of data points. As a cup model for check of the shapes of patterns is made of paper, it is assumed that the surface of the model is composed of several developable surfaces. We claimed that a developable surface can be determined by two curves included in it. The design process of a two-piece brassiere cup can be converted to the optimization problem, whose objective function is the error between the cup shape and its data points. In order to calculate the error, we proposed a method to divide a data cloud into two clouds: evaluated by the lower cup, or evaluated by the upper cup. It was experimentally verified that the cup shape calculated by our proposed method reproduced the given data points well. Our proposed method will be useful for efficient design of not only patterns of a brassiere cup but also plate parts of a structure consisting of developable surfaces.
